---
title: "Tidytext"
author: "Justin Minsk"
date: "2017-11-08"
tags: ["R", "tidytext", "tm", "wordcloud"]
catagory: ["R"]
---
# Tidytext 
Tidytext is a great set of packages that combined with a few other packages and some text can allow you to create some great text analysis.

```{r, warning=FALSE, message=FALSE}
library(tidytext)
library(tm)
library(wordcloud)
library(stringr)
library(dplyr)
library(knitr)
library(gutenbergr)
```

# Gutenbergr

This package contains a lot of books we can use to start out text analysis.

```{r, warning=FALSE, message=FALSE}
gutenberg_works(author == str_extract(author, "Poe, Edgar Allan"))
#see Poes work's IDs

df <- gutenberg_download(10031)
#get the complete poetical works of Edgar Allan Poe
```

Now that we have the book in a data frame we can start to break it down into words.

```{r, warning=FALSE, message=FALSE}
words_df <- df%>%
  unnest_tokens(word, text)
#split the lines into words
```

Then we can remove common words which are not useful in an analysis.

```{r, warning=FALSE, message=FALSE}
words_df <- words_df%>%
  filter(!(word %in% stop_words$word))
#get rid of common words that are not unique (the, a, etc.)

words_df <- words_df%>%
  filter(!word == "thy" & !word == "thou" & !word == "thee")
#some older words not in out stop_word list that are not useful
```

# Wordcloud

A good visual representation of words and their counts is a wordcloud which we can do in R.
First we need to get the count.

```{r, warning=FALSE, message=FALSE}
words_free <- words_df%>%
  group_by(word)%>%
  summarise(count = n())%>%
  arrange(-count)
#make a count of the word
```

Then with one line from the wordcloud package we can make a word cloud.

```{r, warning=FALSE, message=FALSE}
wordcloud(words_free$word, words_free$count, min.freq = 25)
#make a word cloud
```

